---
title: "EDA"
author: "Serkan Oral"
date: '2022-05-25'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages

```{r include=FALSE}
library(tidyverse)
library(tidymodels)
library(naniar)
library(skimr)
library(patchwork)
library(vip)



```

Importing Data

```{r include=FALSE}

train_data <- read_csv("Data/train.csv")
test_data <- read_csv("Data/test.csv")
sample <- read_csv("Data/sample_submission.csv")

```

```{r}
glimpse(train_data)
```

```{r}
gg_miss_var(train_data)
```

```{r}
train_data %>% 
  skim()
```

```{r}

train <- train_data %>% 
  mutate(Cabin_original = Cabin) %>% 
  separate(Name, into =c("First_name", "Last_name")) %>% 
  separate(Cabin, into = c("Cabin_1", "Cabin_2", "Cabin_3" )) %>% 
  mutate_if(is.character, factor)




train %>% 
  drop_na(Last_name) %>% 
  filter(Last_name == "Barbes") %>% 
  count(Transported)


test <- test_data %>% 
  mutate(Cabin_original = Cabin) %>% 
  separate(Name, into =c("First_name", "Last_name")) %>% 
  separate(Cabin, into = c("Cabin_1", "Cabin_2", "Cabin_3" )) %>% 
  mutate_if(is.character, factor)


```

NA's are almost distributed evenly. So we will check each feature and decide how to impute the NA values

# AGE

```{r}
train %>%
  drop_na(Age) %>% 
  ggplot(aes(Age, fill = Transported))+
  geom_histogram(binwidth = 1)
```

```{r}
train %>%
filter(is.na(Age)) %>%
count(Transported)
```

We will use Random Forest to replace NA's

# Room Service

```{r}

train %>%
  drop_na(RoomService) %>% 
  ggplot(aes(RoomService , fill = Transported))+
  geom_histogram() 
```

# **DESTINATION**

```{r}
train %>%
count(Destination, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Destination)) %>%
count(Transported)

train %>%
filter(!is.na(Destination)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(Destination) %>%
ggplot(aes(Destination, fill = Transported)) +
geom_bar()
```

```{r}
train %>%
drop_na(Destination,Age) %>%
ggplot(aes(Age,Destination, fill = Transported)) +
geom_boxplot() + coord_flip()
```

# Food Court

```{r}
train %>%
count(FoodCourt, sort = TRUE)
```

```{r}
train %>%
filter(is.na(FoodCourt)) %>%
count(Transported)

train %>%
filter(!is.na(FoodCourt)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(FoodCourt) %>%
ggplot(aes(FoodCourt, fill = Transported)) +
geom_histogram()
```

```{r}
train %>%
drop_na(FoodCourt) %>%
ggplot(aes(FoodCourt +1 , fill = Transported)) +
geom_histogram() + scale_x_log10()
```

# SPA

```{r}
train %>%
count(Spa, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Spa)) %>%
count(Transported)

train %>%
filter(!is.na(Spa)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(Spa) %>%
ggplot(aes(Spa, fill = Transported)) +
geom_histogram()
```

```{r}
train %>%
drop_na(Spa) %>%
ggplot(aes(Spa +1, fill = Transported)) +
geom_histogram() + scale_x_log10()
```

```{r}
train %>%
filter(Spa ==0) %>%
count(Transported)

train %>%
filter(Spa ==1) %>%
count(Transported)

train %>%
filter(Spa ==2) %>%
count(Transported)
```

# VR Deck

```{r}
train %>%
count(VRDeck, sort = TRUE)
```

```{r}
train %>%
filter(is.na(VRDeck)) %>%
count(Transported)


train %>%
filter(!is.na(VRDeck)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(VRDeck) %>%
ggplot(aes(VRDeck, fill = Transported)) +
geom_histogram()
```

```{r}
train %>%
drop_na(VRDeck) %>%
ggplot(aes(VRDeck+1, fill = Transported)) +
geom_histogram()+ scale_x_log10()
```

```{r}
train %>%
filter(VRDeck ==6) %>%
count(Transported)
```

# CABIN

```{r}
train %>%
count(Cabin_original, sort = TRUE)

```

```{r}
train %>%
filter(is.na(Cabin_original)) %>%
count(Transported)

train %>%
filter(!is.na(Cabin_original)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(Cabin_original) %>%
ggplot(aes(Cabin_original, fill = Transported)) +
geom_bar()
```

# CABIN_1

```{r}
train %>%
count(Cabin_1, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Cabin_1)) %>%
count(Transported)

train %>%
filter(!is.na(Cabin_1)) %>%
count(Transported)

train %>%
filter(Cabin_1 == "A") %>%
count(Transported)

train %>%
filter(Cabin_1 == "D") %>%
count(Transported)
```

```{r}
train %>%
drop_na(Cabin_1) %>%
ggplot(aes(Cabin_1, fill = Transported)) +
geom_bar()
```

# CABIN_2

```{r}
train %>%
count(Cabin_2, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Cabin_2)) %>%
count(Transported)

train %>%
filter(!is.na(Cabin_2)) %>%
count(Transported)

train %>%
filter(Cabin_2 == "269") %>%
count(Transported)
```

```{r}
train %>%
drop_na(Cabin_2) %>%
ggplot(aes(as.numeric(Cabin_2), fill = Transported)) +
geom_histogram() + labs(x = "Cabin_2") 
```

# CABIN_3

```{r}
train %>%
count(Cabin_3, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Cabin_3)) %>%
count(Transported)

train %>%
filter(!is.na(Cabin_3)) %>%
count(Transported)

train %>%
filter(Cabin_3 == "P") %>%
count(Transported)

train %>%
filter(Cabin_3 == "S") %>%
count(Transported)
```

```{r}
train %>%
drop_na(Cabin_3) %>%
ggplot(aes(Cabin_3, fill = Transported)) +
geom_bar()
```

# FIRST NAME

```{r}
train %>%
count(First_name, sort = TRUE)
```

```{r}
train %>%
filter(is.na(First_name)) %>%
count(Transported)

train %>%
filter(!is.na(First_name)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(First_name) %>%
ggplot(aes(First_name, fill = Transported)) +
geom_bar()
```

# LAST NAME

```{r}
train %>%
count(Last_name, sort = TRUE)
```

```{r}
train %>%
filter(is.na(Last_name)) %>%
count(Transported)

train %>%
filter(!is.na(Last_name)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(Last_name) %>%
ggplot(aes(Last_name, fill = Transported)) +
geom_bar()
```

# Home Planet

```{r}
train %>%
count(HomePlanet, sort = TRUE)
```

```{r}
train %>%
filter(is.na(HomePlanet)) %>%
count(Transported)

train %>%
filter(!is.na(HomePlanet)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(HomePlanet) %>%
ggplot(aes(HomePlanet, fill = Transported)) +
geom_bar()
```

# VIP

```{r}
train %>%
count(VIP, sort = TRUE)
```

```{r}
train %>%
filter(is.na(VIP)) %>%
count(Transported)

train %>%
filter(!is.na(VIP)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(VIP) %>%
ggplot(aes(VIP, fill = Transported)) +
geom_bar()
```

# Shopping Mall

```{r}
train %>%
count(ShoppingMall, sort = TRUE)
```

```{r}
train %>%
filter(is.na(ShoppingMall)) %>%
count(Transported)

train %>%
filter(!is.na(ShoppingMall)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(ShoppingMall) %>%
ggplot(aes(ShoppingMall +1 , fill = Transported)) +
geom_histogram() + scale_x_log10()
```

# Cryo Sleep

```{r}
train %>%
count(CryoSleep, sort = TRUE)
```

```{r}
train %>%
filter(is.na(CryoSleep)) %>%
count(Transported)

train %>%
filter(!is.na(CryoSleep)) %>%
count(Transported)
```

```{r}
train %>%
drop_na(CryoSleep) %>%
ggplot(aes(CryoSleep, fill = Transported)) +
geom_bar()
```

What to do with NA values

AGE - Random Forest

ROOMSERVICE - 3 - maybe log transformation +1

Destination - "PSO J318.5-2255"

Foodcourt - 0 - maybe log transformation +1

SPA - 2 - maybe log transformation +1

VRDeck - 6 - maybe log transformation +1

CABIN_1 - A

CABIN_2 - "269"

CABIN_3 - KNN

Cabin_original - CABIN_1+ CABIN_2 + CABIN_3

First_name - unknown

Last_name - unknown

HomePlanet - Mars

VIP - TRUE

ShoppingMall - 0 - maybe log transformation +1

Cryosleep - FALSE
