---
title: "Model"
author: "Serkan Oral"
date: '2022-05-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse)
library(tidymodels)
library(naniar)
library(skimr)
library(patchwork)
library(vip)
```


Splitting Data

```{r}
train$Transported <- as.factor(train$Transported)
train$CryoSleep <- as.factor(train$CryoSleep)
train$VIP <- as.factor(train$VIP)

test$CryoSleep <- as.factor(test$CryoSleep)
test$VIP <- as.factor(test$VIP)

set.seed(123)
split <- initial_split(train, strata = Transported)
train_t <- training(split)
test_t <- testing(split)

```


Recipe

What to do with NA values
AGE - Random Forest
ROOMSERVICE - 3 - maybe log transformation +1
Destination - "PSO J318.5-2255"
Foodcourt - 0 - maybe log transformation +1
SPA - 2 - maybe log transformation +1
VRDeck - 6 - maybe log transformation +1
CABIN_1 - A
CABIN_2 - "269"
CABIN_3 - KNN
Cabin_original - CABIN_1+ CABIN_2 + CABIN_3
HomePlanet - Mars
VIP - TRUE
ShoppingMall - 0 - maybe log transformation +1
Cryosleep - FALSE

```{r}
set.seed(123)
rec <- train_t %>%
recipe(Transported ~.)%>%
step_novel(all_nominal_predictors()) %>% 
step_unknown(First_name,Last_name) %>% 
step_impute_bag(Age) %>% 
step_impute_knn(all_predictors(),neighbors = 5) %>% 
step_log(RoomService, FoodCourt,Spa, VRDeck,ShoppingMall,offset = 1) %>% 
step_normalize(all_numeric_predictors()) %>% 
step_nzv(all_numeric_predictors()) 
  
  
```




```{r}
preped_rec <- rec %>% prep()

preped_rec %>% bake(new_data = NULL) %>% 
  gg_miss_var()

```

```{r}
rf_spec <- rand_forest(min_n = tune(), mtry =tune(), trees = 1000) %>%
set_engine("ranger")%>%
set_mode("classification")
```


```{r}
rf_wf <- workflow() %>%
add_recipe(rec,blueprint = hardhat::default_recipe_blueprint(allow_novel_levels = TRUE))%>%
add_model(rf_spec)
```

```{r}
set.seed(123)
rf_grid <- grid_latin_hypercube(min_n(), finalize(mtry(),train_t), size = 50)
```

```{r}

kfold <- vfold_cv( train_t)

doParallel::registerDoParallel()

set.seed(234)
rf_res <- tune_grid(object = rf_wf,resamples = kfold,grid = rf_grid,control = control_grid(save_pred = TRUE),metrics = metric_set(accuracy))

rf_final_wf <- finalize_workflow(rf_wf, select_best(rf_res))
```


```{r}


doParallel::registerDoParallel()

rf_fit <- fit(rf_final_wf, train)
```


```{r}

test_t <- preped_rec %>% bake(new_data = test_t)
predict(rf_fit, test_t) %>% 
  bind_cols(test_t) %>% 
  select(.pred_class, Transported) %>% 
  conf_mat(Transported, .pred_class)
```

```{r}

set.seed(123)
submission <- predict(rf_fit, test) %>% 
  bind_cols(test) %>% 
  select(PassengerId, .pred_class) %>% 
  rename(Transported = .pred_class)

submission$PassengerId <- as.character(submission$PassengerId)
submission$Transported <- str_to_title(as.character(submission$Transported))

write_csv(submission,file = "Submission.csv")
```




